---
title: "Lab Assignment Questions"
format: html
echo: false
---


{{< var Lab.assignments.quizInfo >}}

# Rubric

{{< var Lab.assignments.rubricInfo >}}

```{r include=FALSE}

library(knitr)
```

```{r}
#| label: tbl-schedule
#| tbl-cap: "Lab Quiz Rubric"
#| tbl-colwidths: [10,35,35,10]

rubric <- read.csv(file = '../../sheets/Rubric.csv',sep='|')
kable(rubric, col.names = gsub("[.]", " ", names(rubric)))

```

# Quiz Questions


Unless otherwise specified, numeric answers have a margin of error of 0.01, so give all responses to at least the hundredths place.

(@) Which projection did we choose for the **BC_Census_Data** feature dataset and why?  Why can't we just work with the simply analytics data as is? [Hint](instructions.qmd#importing-the-census-data)

(@) We used the clip tool to ensure we don't  ____ population density in the coastal Subdivisions. [Hint](instructions.qmd#clip-the-bc_census_data-layer)


* Overestimate
* Underestimate
* Correctly Calculate

(@) What was the reasoning behind Stats Canada updating from the old Rural/Urban to the Population Centre and Rural Area classification method? [Hint](instructions.qmd#the-revised-classification)

* The old classification was treating small towns the same a large metro areas
* Population Center sounds better than Urban Area
* They didn't change the classification

(@) The Select by ____ tool lets us use SQL (Structured Query Language) to define expressions for querying vector data. [Hint](instructions.qmd#applying-the-classification)

(@) What measurement scale would population density attribute be on? [Hint](instructions.qmd#applying-the-classification) [Hint-2](https://geos270.github.io/LectureSlides/Phenomena_and_Data_Types/Slides.html#/summary-types-of-data)

- Nominal
- Ordinal
- Interval (Discrete)
- Interval (Continuous)
- Ratio (Discrete)
- Ratio (Continuous)

(@) What best describes the Population Center and Rural Area Classification attribute we created? [Hint](instructions.qmd#applying-the-classification)

- Quantitative data
- Qualitative data
- both
- neither

(@) Box plots are most useful for looking at frequency distributions. [T/F] [Hint](instructions.qmd#plotting-relationships)

(@) In which Population Centre and Rural Area class does the the largest proportion of BC's population live? [Hint](instructions.qmd#plotting-relationships)

- Large Urban Population Centre
- Rural
- Small Population Centre
- Medium Population Centre

(@) What  percent  of BC's overall population lives in Rural Areas?  Round your answer to the nearest percent.  *Hint* Sum the four classes to get the total population. [Hint](instructions.qmd#plotting-relationships)

(@) What is the median value for the percentage of income that people in Rural areas spend on food?  Round to the nearest tenth percent. [Hint](instructions.qmd#plotting-relationships)

(@) How does classifying the data help us reveal patterns compared to what we see in the scatter plot?  Does the r2 score indicate a relationship in the scatter plot?  What conclusions can you draw about the proportion of income spent on food by people in different regions from looking at the box plot? [Hint](instructions.qmd#benefits-of-data-classification)

(@) Submit your Bar Chart. [Hint](instructions.qmd#styling-your-visualizations)

(@) Submit your Box plot. [Hint](instructions.qmd#styling-your-visualizations)

