---
title: "Lab Assignment Questions"
format: html
echo: false
---


{{< var Lab.assignments.quizInfo >}}

# Rubric

{{< var Lab.assignments.rubricInfo >}}

```{r include=FALSE}

library(knitr)
```

```{r}
#| label: tbl-schedule
#| tbl-cap: "Lab Quiz Rubric"
#| tbl-colwidths: [10,35,35,10]

rubric <- read.csv(file = '../../sheets/LabRubric.csv',sep='|')
kable(rubric, col.names = gsub("[.]", " ", names(rubric)))

```

# Quiz Questions


Unless otherwise specified, numeric answers have a margin of error of 0.01, so give all responses to at least the hundredths place.


(@) What does the example presented in Ludwin et al. 2005 say about the value that the sciences have historically attributed to traditional knowledge when it comes to understanding our world?  [Hint](instructions.qmd#traditional-knowledge-and-records-of-past-tsunamis)


(@) The maximum wave height recorded at Tofino was only ____ meters.  Despite this, wave heights exceeded 8 meters in Port Alberni. [Hint](instructions.qmd#unique-geography)


(@) Look back at Ludwin et al. 2005, specifically at the story of Pachena Bay (bottom pg 142 to top of pg 143).  You can find a [full transcription here](https://pnsn.org/outreach/native-american-stories/other-stories/the-tsunami-at-anaqtl-a-or-pachena-bay).  Find Pachena Bay on google maps.  Where is it relative to Port Alberni?  What can you infer from this story, the account in Fine et al (2008), and the simulation of wave heights about how a megathrust earthquake occurring just off of the coast of Vancouver Island would impact Port Alberni? [Hint](instructions.qmd#simulated-wave-heights)


(@) Why do we use a feature dataset to hold all our input layers? [Hint](instructions.qmd#port-alberni-data)

* No reason
* So everything is neatly grouped in one folder
* To ensure all our vector data is in the same projection, the feature dataset will automatically re-project our vector data when importing
* To ensure all our vector and raster data is in the same projection, the feature dataset will automatically re-project our vector and raster data when importing

(@) Why are we using model builder for this analysis?  Select all that apply [Hint](instructions.qmd#automating-with-model-builder)

* Your analysis is easily repeatable when using model builder
* You can easily update your analysis
* You can visualize your workflow
* You can share your workflow with others

(@) How many **km** of roads are at risk?  Rounded to the nearest tenth km is fine.  *Hint* Open the attribute, of PA_Roads_Flood, click right Click Shape_Length >> Statistics to find the sum.  **Note** make sure to use the answer for the model run with the 10m threshold. [Hint](instructions.qmd#clip-the-roads-layer)


(@) How many **km** of roads are at risk after updating the model to account for the new wave height (15m) estimates? Rounded to the nearest tenth km is fine.  **Note** this answer will be higher than your answer to the question above because we increased the threshold. [Hint](instructions.qmd#new-wave-estimates)


(@) How many properties (of any kind) are at risk of flooding? **Note** make sure to use the answer for the model run with the 15m threshold. [Hint](instructions.qmd#new-wave-estimates)


(@)  How many people are potentially at risk of displacement?  **Round up to the nearest whole number** [Hint](instructions.qmd#new-wave-estimates)


(@) Why were you instructed to round the answer to the question above? [Hint](instructions.qmd#new-wave-estimates)


- Population counts are continuous data
- Population counts are discrete data
- Population counts are qualitative data
- Population counts are interval data


(@) Upload your **PA_RiskAssessment_Model.pdf** [Hint](instructions.qmd#export-your-model)

(@) Upload your **Properties_at_Risk_Chart.pdf** [Hint](instructions.qmd#supporting-figures)

(@) Upload your **PA_RiskAssessment_Final_Map.pdf** [Hint](instructions.qmd#map-the-assessment)
