---
title: "Lab Assignment Questions"
format: html
echo: false
---


{{< var Lab.assignments.quizInfo >}}

# Rubric

{{< var Lab.assignments.rubricInfo >}}

```{r include=FALSE}

library(knitr)
```

```{r}
#| label: tbl-schedule
#| tbl-cap: "Lab Quiz Rubric"
#| tbl-colwidths: [10,35,35,10]

rubric <- read.csv(file = '../../sheets/LabRubric.csv',sep='|')
kable(rubric, col.names = gsub("[.]", " ", names(rubric)))

```

# Quiz Questions


Unless otherwise specified, numeric answers have a margin of error of 0.01, so give all responses to at least the hundredths place.


(@) List the risk classification score for each of the shelters.  If the shelter did not have a risk classification, you can list it as "N/A"  [Hint](instructions.qmd#risk-level-of-shelter-locations)


Echo Community Centre:
AW Neil Elementary:
5100 Tebo Ave:


(@) Submit a .pdf of the model you created to identify the inundation zone. [Hint](instructions.qmd#your-model)


(@) Submit a .pdf of the map you created to showing the updated inundation zone and shelter locations. [Hint](instructions.qmd#final-map)


(@) Write a paragraph or two comparing the method used in Module 5 (previous method) model to identify the Inundation Zone vs. the method used in this Module 6 (this assignment) to identify the Inundation Zone.  **Things to consider:** What tools/steps were used in each model?  Which do you think produces a more useful result?  What are some potential pros/cons of the  different methods? [Hint](instructions.qmd#redoing-the-risk-assessment)


(@) Read the highlighted portions of [Chae et al. (2015)](readings/Chae_et_al_2015.pdf) on racism and health outcomes.  Then use this information to a couple paragraphs outlining what they found, how the type of data they used can be a useful alternative for traditional metrics, and what are some potential limitations to this type of research.